Experience Report: Haskell in Computational Biology

### 2012-07-03 icfp29ex-daniels.tex
for reference, submitted files are included.

GHC's profiler assigns costs not to functions but to ``cost
centers'' \cite{sansom-pj}.
In GHC~7.0, which we used 
for most of MRFy's development, 
cost-center annotations must be added manually
to nested functions.
The annotations
made our code so ugly that we felt compelled to
remove them as soon as possible.
Nonetheless, GHC's profiler led us to the performance
improvements discussed in \secref{perf}.
We~miss valgrind, whose profiler gives useful information
without \emph{any} annotations.
GHC~7.4 provides much
better profiling tools, which eliminate most of these obstacles,
and we look forward to further profiling MRFy.

>>>>

We~had quite some difficulty profiling, but we hope that
this difficulty may be mitigated by new profiling tools released early
in~2012 with
GHC~7.4.
GHC assigns costs to ``cost centers'' \cite{sansom-pj},
and
in GHC~7.0, which we used 
for most of MRFy's development, 
cost-center annotations had to be added manually
to nested functions.
Although these annotations
made our code so ugly that we felt compelled to
remove them, they did enable us to improve the performance of~\verb+vee'+ as
discussed in \secref{perf}.
%We~miss valgrind, whose profiler gives useful information
%without \emph{any} annotations.
GHC~7.4 provides 
more sophisticated profiling tools, which we look forward to using.
Difficulties using Cabal to enable profiling of installed libraries
may remain.
